A general model of microbial interactions in a chemostat.

### 2019-11-19 tex/Tracking.tex
title change
modified intro

\title{A Model of Microbial Interactions in a Chemostat Setting : Analysis and Application}

@@

Microbial communities and their interactions play a central role in the understanding of microbial ecosystems \cite{West2007}, and a current challenge is integrating genetic sequencing data in a deterministic modelling framework \cite{Widder2016,WADE201664}. A thorough review in current methodologies in the deterministic modelling approaches of microbial community dynamics is presented by Song \textit{et al.} \cite{Song2014}. Using their terminology this articles deals with population-based approaches where species are taken as the interacting units. Particularly the model here studied could be classified as a stoichiometric model of multiple species and at the same time as a generalized Lotka Volterra Model \cite{Hernandez-Bermejo1997}.

@@

In the past years considerable efforts have been made to measure the bacterial community composition. Tests such as fluorescence in situ hybridization, polymerase chain reaction (PCR) dependent techniques, and PCR independent techniques for the analysis of DNA, RNA, proteins and metabolites have become a standard tool for studying  microbial diversity\cite{FERRERA2016790}.

The objective of this article is to show a method to predict the reactor performance based on any technique that can track the species relative abundances through time. This work revisits the model proposed by Dumont et al \cite{Dumont2016} in which a model with intra and inter species interactions were they claimed coexistence of two species consuming the same substrate: The rigorous mathematical and numerical analysis of this work states the contrary. However, using a different set of parameters than the ones proposed on their article, the model proposed becomes very rich in steady states, and different coexistences may emerge depending on operational parameters of the working chemostat. Their approach suffers from a quadratic growing number of parameters on the number of species considered, thus its scope of applicability for diverse ecosystems seems limited.

In the present paper this difficulty is overcame by generalizing their interactions approach and using method of optimal tracking for parameter identification, where the growth rate of each species is modulated by a constrained regular control of the system.  The regular control is composed of a feedback part on the species state variable, and a feed forward part, or tracking, on the abundances of each species. The main novelty of the article lies in proposing/testing/using microbial interactions as the driver of the reactor's performance  through an optimal control approach.

The article is divided in a first section that re-examines the properties of the work of Dumont \textit{et al.} \cite{Dumont2016}, and a second section that generalizes their approach.

>>>>

\title{A general model of microbial interactions in a chemostat.}

@@

Microbial communities and their interactions play a central role in the understanding of microbial ecosystems \cite{West2007}, and a current challenge is integrating genetic sequencing data in a deterministic modelling framework \cite{Widder2016,WADE201664}. A thorough review in current methodologies in the deterministic modelling approaches of microbial community dynamics is presented by Song \textit{et al.} \cite{Song2014}. Using their terminology this articles deals with population-based approaches where species are taken as the interacting units.

@@

In the past years considerable efforts have been made to measure the bacterial community composition. Tests such as fluorescence in situ hybridization, polymerase chain reaction (PCR) dependent techniques, and PCR independent techniques for the analysis of DNA, RNA, proteins, and metabolites have become a standard tool for studying  microbial diversity\cite{FERRERA2016790}.

The main contribution of this article is a procedure to integrate the microbial community measurements in chemostat models, based on any technique that can quantify the species abundances through time. This is a first step towards developing predictive models of a reactor's performance based on the microbial community structure.

As a departing point the work of Dumont et al.\cite{Dumont2016} is reinspected in section 2. They model a chemostat experiment where nitrification takes place by considering a generalized Lotka-Volterra (gLV) model \cite{Hernandez-Bermejo1997} coupled with a substrate limited growth expression. Section 3 deals with the mathematical analysis of their model. It is shown that the number of possible equilibrium points grows exponentially with the number of species. Finally after a numerical analysis it is conjectured that there always exists a single stable equilibrium point depending on the operational parameters.

Section 4 is the article's most original contribution. The concept of interaction function is developed such that it generalizes the gLV model. For the identification of the interaction function a method of optimal tracking was adapted: The growth rate of each species is modulated by a constrained regular control of the system. The regular control is composed of a feedback part on the species state variable, and a feed forward part, or tracking, on the measurement of abundances of each species.

In section 5 the methodology from section 4 is applied to the data from the experiments perform by Dumont et al \cite{Dumont2009}. Finally, a discussion on the scope of the method, its shortcomings and perspectives is presented.
